prolfqua - An R-package for Analysing Proteomics Label Free Quantification Experiments

### 2022-03-18 inst/MyArticle/paper.Rmd
Edit authors

---
title: prolfqua - An R-package for Analysing Proteomics Label Free Quantification Experiments
author: 
  - name: Witold Wolski
    affil: 1; 2
    orcid: '0000-0002-6468-120X'
  - name: Paolo Nanni
    affil: 1
    orcid: '0000-0001-8429-3557'
  - name: Jonas Grossmann
    affil: 1; 2
    orcid: '0000-0002-6899-9020'
  - name: Maria D'Errico
    affil: 1; 2
    orcid: '0000-0001-9467-9058'
  - name: Ralph Schlapbach
    affil: 1
    orcid: '0000-0002-7488-4262'
  - name: Christian Panse
    affil: 1; 2
    orcid: '0000-0003-1975-3064'
affiliation:
  - num: 1
    address: Functional Genomics Center Zurich (FGCZ) - Swiss Federal Institute of Technology in Zurich and University of Zurich
  - num: 2
    address: Swiss Institute of Bioinformatics (SIB)
output: 
  bookdown::pdf_document2:
    toc: true
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
abstract: |
  Protein mass spectrometry is widely used for quantitative proteomics
  studies and in particular for relative protein quantification.
  Nevertheless, there is still a need for a flexible and easy-to-use, 
  transparently supporting a variety of well principled statistical
  inference procedures data analysis application programmer interface
  in R. The `r BiocStyle::Githubpkg("fgcz/prolfqua")` R package integrates
  essential steps of the mass spectrometry-based label-free quantification
  data analysis workflow as: quality control, data normalization, protein
  aggregation, statistical modeling, hypothesis testing, and sample size
  estimation.
  We use `r BiocStyle::Githubpkg("fgcz/prolfqua")` to visualize and model
  simple experimental designs with a single explanatory variable and complex
  experiments with multiple factors.
  Furthermore, we use `r BiocStyle::Githubpkg("fgcz/prolfqua")` to benchmark
  data acquisition, data preprocessing or data modeling methods. Furthermore,
  we apply `r BiocStyle::Githubpkg("fgcz/prolfqua")` to develop highly
  customizable, visually appealing, and interactive data analysis reports
  in PDF or HTML format.
  The R package is available through https://github.com/fgcz/prolfqua.
---

>>>>

---
title: prolfqua - An R-package for Analysing Proteomics Label Free Quantification Experiments
author: 
  - Witold E. Wolski^[Functional Genomics Center Zurich (FGCZ) - Swiss Federal Institute of Technology in Zurich \| University of Zurich]
  - Paolo Nanni$^*$
  - Jonas Grossmann$^*$
  - Maria d'Errico$^*$
  - Ralph Schlapbach$^*$
  - Christian Panse$^*$
output: 
  bookdown::pdf_document2:
    toc: true
bibliography: bibliography.bib
editor_options: 
  chunk_output_type: console
abstract: |
  Protein mass spectrometry is widely used for quantitative proteomics
  studies and in particular for relative protein quantification.
  Nevertheless, there is still a need for a flexible and easy-to-use, 
  transparently supporting a variety of well principled statistical
  inference procedures data analysis application programmer interface
  in R. The `r BiocStyle::Githubpkg("fgcz/prolfqua")` R package integrates
  essential steps of the mass spectrometry-based label-free quantification
  data analysis workflow as: quality control, data normalization, protein
  aggregation, statistical modeling, hypothesis testing, and sample size
  estimation.
  We use `r BiocStyle::Githubpkg("fgcz/prolfqua")` to visualize and model
  simple experimental designs with a single explanatory variable and complex
  experiments with multiple factors.
  Furthermore, we use `r BiocStyle::Githubpkg("fgcz/prolfqua")` to benchmark
  data acquisition, data preprocessing or data modeling methods. Furthermore,
  we apply `r BiocStyle::Githubpkg("fgcz/prolfqua")` to develop highly
  customizable, visually appealing, and interactive data analysis reports
  in PDF or HTML format.
  The R package is available through https://github.com/fgcz/prolfqua.
---
